Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
edits

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotive development directly impacts their access to social information, here operationalized as the presence of the faces and wrists of their caregiver. We found that children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically impacted the proportion of faces and wrists that were available in the child's visual field. Thus, infants' postural and locomotive developments are mediating factors that explain some of the age-related changes in the proportion of faces and wrists/hands that are visually available to infants. Broadly, this work suggests that motoric developments mediate how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

>>>>

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotive development directly impacts their access to social information, here operationalized as the presence of the faces and wrists of their caregiver. We found that children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically impacted the proportion of faces and hands that were available in the child's visual field. Thus, infants' postural and locomotive developments are mediating factors that explain some of the age-related changes in the proportion of faces and wrists/hands that are visually available to infants. Broadly, this work suggests that motoric developments mediate how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.tex
edits

We used a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information, here operationalized as the presence of the faces and
wrists of their caregiver. We found that children's posture and
orientation towards their caregiver changed systematically across age,
and that both of these factors dramatically impacted the proportion of
faces and wrists that were available in the child's visual field. Thus,
infants' postural and locomotive developments are mediating factors that
explain some of the age-related changes in the proportion of faces and
wrists/hands that are visually available to infants. Broadly, this work
suggests that motoric developments mediate how infants experience their
visual world and the social information in it: infants that are sitting
and standing have a different view of their world, the people in it, and
the actions that are being performed.

>>>>

We used a head-mounted camera to explore how children's postural and
locomotive development directly impacts their access to social
information, here operationalized as the presence of the faces and
wrists of their caregiver. We found that children's posture and
orientation towards their caregiver changed systematically across age,
and that both of these factors dramatically impacted the proportion of
faces and hands that were available in the child's visual field. Thus,
infants' postural and locomotive developments are mediating factors that
explain some of the age-related changes in the proportion of faces and
wrists/hands that are visually available to infants. Broadly, this work
suggests that motoric developments mediate how infants experience their
visual world and the social information in it: infants that are sitting
and standing have a different view of their world, the people in it, and
the actions that are being performed.
